---
title: "Writing Functions"
author: "Lizbeth Gomez"
date: "10/24/2019"
output: github_document
---

Class slides at  [Session 15 - Writing functions](https://p8105.com/writing_functions.html) 
Some notes from the slides:
functions have:
Arguments (input)
body (code)
return (fucntion's product)


Conditional execution:
proper fornmating of if statements 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(rvest)
```

## Getting started

writing fucntions

```{r}
x= rnorm (n=30, mean =4, sd =2.3)
x_again= rnorm (n=30, mean =6, sd =.3)
y= rnorm (n=30, mean =24, sd =.3)
(x- mean(x))/ sd(x)
(x_again- mean(x_again))/ sd(x_again)


```

Now a fucntion:
the x argument insude the fucntion
even if there is an x in the environment the x will be from the function
```{r}
z_scores = function(x) {
  
  if(!is.numeric(x)) {
    stop("x should be numeric")
  } else if (length(x <3)) {
    stop("x should be longer than 3")
  }
  
  (x - mean(x)) / sd(x)
  
  
}

```

Trying out the function

```{r, error= TRUE}
z_scores(x=3)
z_scores (x=y)
z_scores ("my name is liz")
z_scores (x = c(TRUE, TRUE, FALSE, TRUE))
z_scores(x= iris)

```

## multiple outputs

no lists for now


```{r}

mean_and_sd = function(input_x) {
  
  if (!is.numeric(input_x)) {
    stop("Argument x should be numeric")
  } else if (length(input_x) < 3) {
    stop("Cannot be computed for longer than 3")
  }
  
  mean_x = mean(input_x)
  sd_x = sd(input_x)

  list(mean = mean_x, 
       sd = sd_x)
}
```

#multiple inputs

```{r}

sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)
sim_data %>%  ggplot (aes(x=x, y=y)) +geom_point()
ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]  # intercept
beta1_hat = coef(ls_fit)[2]  # slope
```


```{r}
sim_regression = function(n, beta0, beta1) {
  
sim_data = tibble(
  x = rnorm(n, mean = 1, sd = 1),
  y = beta0 + beta1 * x + rnorm(n, 0, 1)
)

ls_fit = lm(y ~ x, data = sim_data)
tibble(
  beta0_hat = coef(ls_fit)[1],  # intercept
  beta1_hat = coef(ls_fit)[2]  # slope
)
}

sim_regression(n=3000, beta0 = 17, beta1 = -3)


sim_regression(n=3000, beta0 = 17, beta1 = -3) # can change some of the arguments and not others, as well as write them in oder without haveing to equal the variables


```

